\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-05-13 doc/paper.tex
extending Appendix B

\end{enumerate}   
\section{Tests}
Comparisons against existing spectrum generators to test for deviations, e.g. the tests against MSSM and NMSSM (and E6SSM?).

Comparisons against existing spectrum generators and SARAH generated spheno code for speed.

>>>>

\section{Numeric tests}

For checking the correctness of \fs's generated spectrum generators
extensive unit tests against Softsusy's MSSM, and NMSSM
implementations (both $Z_3$-invariant and $Z_3$-violating variants)
were done: We checked mass matrices, EWSB equations, one- and two-loop
$\beta$-functions, one- and two-loop self-energies and one- and
two-loop tadpoles and found all to agree within double machine
precision.  We also compared the overall pole mass spectrum after the
full fixed-point iteration has finished, and found the spectra to
agree at the sub-permille level.  Analytic tests of the $R$-symmetric
low-energy model, MRSSM, were done by Philip Diessner and several bugs
in \fs and SARAH were identified and fixed.

TODO: Adding tests against the CE$_6$SSM?

We also compared the run-time of \fs against SPheno, Softsusy and the
SARAH generated MSSM spectrum generator SPhenoMSSM.  The test results
can be found in \secref{Sec:comparison}.
